\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-11-24 main.tex
simple commit
testing something regarding the line lenght

\title{
\bf  \sffamily \LARGE Evolution of cooperation among individuals with limited payoff memory\\}
\date{}
\author{Christian Hilbe, Nikoleta E. Glynatsi, Alex McAvoy}

@@

\begin{abstract}
Repeated games are vastly used in evolutionary game theory to explain
cooperation in a variety of environments. Although existing models have shaped
our understanding of human cooperation, they often work with idealized
assumptions. In an evolutionary process, individuals imitate other individuals
of the population based on their fitness. It is commonly assumed that an
individual computes their fitness after interacting with a representative sample
of the population, and remembering all the interactions they participated in. In
real life, we do not always remember all our interactions, instead we rather
recall our most recent ones.

@@

>>>>

\title{
\bf  \sffamily \LARGE Evolution of cooperation among individuals with limited payoff memory\\}
\date{}
\author{Nikoleta E. Glynatsi, Christian Hilbe, Alex McAvoy}

@@

\begin{abstract}
Repeated games are vastly used in evolutionary ame theory to explain cooperation in a variety of environments. Although existing models have shaped our understanding of human cooperation, they often work with idealized
assumptions. In an evolutionary process, individuals aimitate other individuals
of the population based on their fitness. It is commonly assumed that an
individual computes their fitness after interacting with a representative sample
of the population, and remembering all the interactions they participated in. In
real life, we do not always remember all our interactions, instead we rather
recall our most recent ones.

@@

# This needs an intro, guiding readers into the model.

Just words.
